Evaluating computational methods for modeling off-normal operation of gas centrifuge cascades

### 2018-07-17 experiement.tex

As mentioned, all the further calculations will be compared to the most
favorable configuration to produce \gls{HEU}, where all the available
centrifuges are used in a single large cascade designed to directly produce
\gls{HEU} from natural uranium, with a tails assay close to $0.3w\%$. The design
characteristic of the reference cascade are summarized in Table
\ref{tab:cascade_config}.

@@

The default cascade is the cascade design for normal civilian enrichment
operation, enriching natural uranium to about $3.5w\%$, with a tails assay close
to $0.3w\%$. This cascade will be layered and fed with uranium at higher
enrichment to evaluate the possibility to use them, with little or no tuning, to
produce \gls{HEU}. The characteristics of the default cascade are summarized in
Table \ref{tab:cascade_config}.

>>>>

As mentioned, all the further calculations will be compared to the most
favorable configuration to produce \gls{HEU}, where all the available
centrifuges are used in a single large ideal symmetric cascade designed to
directly produce \gls{HEU} from natural uranium, with a tails assay close to
$0.3w\%$. The design characteristic of the reference cascade are summarized in
Table \ref{tab:cascade_config}.

@@

The default cascade is the ideal symmetric cascade designed for normal civilian
enrichment operation, enriching natural uranium to about $3.5w\%$, with a tails
assay close to $0.3w\%$. This cascade will be layered and fed with uranium at
higher enrichment to evaluate the possibility to use them, with little or no
tuning, to produce \gls{HEU}. The characteristics of the default cascade are
summarized in Table \ref{tab:cascade_config}.
